---
title: "Brown et al. Survival models"
author: "Alissa Brown"
date: "February 28, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, include = FALSE}
x <- c("lme4", "lmerTest", "dplyr", "sjPlot", "gstat", "knitr")
lapply(x, require, character.only = TRUE)

# Data setup
surv <- read.csv("dat_with_soil_updated.csv", stringsAsFactors = FALSE)
colnames(surv)[colnames(surv) == "alt"] <- "elev"

surv$BAtot5 <- surv$BAc5 + surv$BAh5
surv$BAtot5_d <- surv$BAtot5 / (pi*(5^2))
surv$BAc5_d <- surv$BAc5 / (pi*(5^2))
surv$BAh5_d <- surv$BAh5 / (pi*(5^2))

surv <- surv %>% group_by(species) %>% mutate(BAc5_d = scale(BAc5_d))
surv$BAc5_d <- ifelse(is.na(surv$BAc5_d), 0, surv$BAc5_d)
surv <- surv %>% ungroup()

toscale <- c("diam1", "elev", "gap", "org", "cations", "BAh5_d", "BAtot5_d")
surv[, toscale] <- scale(surv[, toscale])

surv %>% select(toscale) %>% summarise_all(list(mean), na.rm=TRUE)
surv %>% select(toscale) %>% summarise_all(funs(sd), na.rm=TRUE)
```

Starting with 5m spatial scale: Run survival models for each environmental covariate, perform model selection, summarize results of best-performing model. Repeat for 10m, 15m, and 20m scales. Then evaluate variograms of best-performing models to check for spatial autocorrelation.

### ELEVATION at 5m scale

```{r, include = FALSE}
# run all competing models
elev.null <- glmer(surv ~ diam1 + elev +
                (1|species), 
               family = binomial(link = "logit"),
               data = surv)
elev.tot.add5 <- update(elev.null, .~. + BAtot5_d)
elev.sep.add5 <- update(elev.null, .~. + BAh5_d + BAc5_d)
elev.tot.int5 <- update(elev.null, .~. + elev*BAtot5_d)
elev.sep.int5 <- update(elev.null, .~. + elev*BAh5_d + elev*BAc5_d)
```

```{r, message = FALSE}
comp.tab.elev5 <- AIC(elev.null, elev.tot.add5, elev.sep.add5, elev.tot.int5, elev.sep.int5)
comp.tab.elev5$delta_AIC <- comp.tab.elev5$AIC - min(comp.tab.elev5$AIC)
comp.tab.elev5 <- cbind(comp.tab.elev5, 
                        BIC(elev.null, elev.tot.add5, elev.sep.add5, elev.tot.int5, elev.sep.int5)[2])
comp.tab.elev5$delta_BIC <- comp.tab.elev5$BIC - min(comp.tab.elev5$BIC)
kable(comp.tab.elev5)
```

```{r, message = FALSE}
# Report model results from best-performing model
tab_model(elev.sep.int5, pred.labels = c("(Intercept)", "Diameter", "Elevation", "Het BA at 5m", "Con BA at 5m", "Het BA * elevation", "Con BA * elevation"), dv.labels = "Sapling survival", digits = 6, show.icc = FALSE, show.re.var = FALSE, title = "Elevation at 5m scale")
```

<br>
<br>

### GAP MEASURE at 5m scale

```{r, include = FALSE}
# run all competing models
gap.null <- glmer(surv ~ diam1 + gap +
                (1|species), 
               family = binomial(link = "logit"),
               data = surv)
gap.tot.add5 <- update(gap.null, .~. + BAtot5_d)
gap.sep.add5 <- update(gap.null, .~. + BAh5_d + BAc5_d)
gap.tot.int5 <- update(gap.null, .~. + gap*BAtot5_d)
gap.sep.int5 <- update(gap.null, .~. + gap*BAh5_d + gap*BAc5_d)
```

```{r, message = FALSE}
comp.tab.gap5 <- AIC(gap.null, gap.tot.add5, gap.sep.add5, gap.tot.int5, gap.sep.int5)
comp.tab.gap5$delta_AIC <- comp.tab.gap5$AIC - min(comp.tab.gap5$AIC)
comp.tab.gap5 <- cbind(comp.tab.gap5, 
                        BIC(gap.null, gap.tot.add5, gap.sep.add5, gap.tot.int5, gap.sep.int5)[2])
comp.tab.gap5$delta_BIC <- comp.tab.gap5$BIC - min(comp.tab.gap5$BIC)
kable(comp.tab.gap5)
```

```{r, message = FALSE}
# Report model results from best-performing model
tab_model(gap.sep.add5, pred.labels = c("(Intercept)", "Diameter", "Gap", "Het BA at 5m", "Con BA at 5m"), dv.labels = "Sapling survival", digits = 6, show.icc = FALSE, show.re.var = FALSE, title = "Gap measure at 5m scale")
```

<br>
<br>

### SOIL ORGANIC MATTER at 5m scale

```{r, include = FALSE}
# run all competing models
org.null <- glmer(surv ~ diam1 + org +
                (1|species), 
               family = binomial(link = "logit"),
               data = surv)
org.tot.add5 <- update(org.null, .~. + BAtot5_d)
org.sep.add5 <- update(org.null, .~. + BAh5_d + BAc5_d)
org.tot.int5 <- update(org.null, .~. + org*BAtot5_d)
org.sep.int5 <- update(org.null, .~. + org*BAh5_d + org*BAc5_d)
```

```{r, message = FALSE}
comp.tab.org5 <- AIC(org.null, org.tot.add5, org.sep.add5, org.tot.int5, org.sep.int5)
comp.tab.org5$delta_AIC <- comp.tab.org5$AIC - min(comp.tab.org5$AIC)
comp.tab.org5 <- cbind(comp.tab.org5, 
                        BIC(org.null, org.tot.add5, org.sep.add5, org.tot.int5, org.sep.int5)[2])
comp.tab.org5$delta_BIC <- comp.tab.org5$BIC - min(comp.tab.org5$BIC)
kable(comp.tab.org5)
```

```{r, message = FALSE}
# Report model results from best-performing model
tab_model(org.sep.add5, pred.labels = c("(Intercept)", "Diameter", "Organic", "Het BA at 5m", "Con BA at 5m"), dv.labels = "Sapling survival", digits = 6, show.icc = FALSE, show.re.var = FALSE, title = "Soil organic matter at 5m scale")
```

<br>
<br>

### CATIONS at 5m scale

```{r, include = FALSE}
# run all competing models
cations.null <- glmer(surv ~ diam1 + cations +
                (1|species), 
               family = binomial(link = "logit"),
               data = surv)
cations.tot.add5 <- update(cations.null, .~. + BAtot5_d)
cations.sep.add5 <- update(cations.null, .~. + BAh5_d + BAc5_d)
cations.tot.int5 <- update(cations.null, .~. + cations*BAtot5_d)
cations.sep.int5 <- update(cations.null, .~. + cations*BAh5_d + cations*BAc5_d)
```

```{r, message = FALSE}
comp.tab.cations5 <- AIC(cations.null, cations.tot.add5, cations.sep.add5, cations.tot.int5, cations.sep.int5)
comp.tab.cations5$delta_AIC <- comp.tab.cations5$AIC - min(comp.tab.cations5$AIC)
comp.tab.cations5 <- cbind(comp.tab.cations5, 
                        BIC(cations.null, cations.tot.add5, cations.sep.add5, cations.tot.int5, cations.sep.int5)[2])
comp.tab.cations5$delta_BIC <- comp.tab.cations5$BIC - min(comp.tab.cations5$BIC)
kable(comp.tab.cations5)
```

```{r, message = FALSE}
# Report model results from best-performing model
tab_model(cations.sep.add5, pred.labels = c("(Intercept)", "Diameter", "Cations", "Het BA at 5m", "Con BA at 5m"), dv.labels = "Sapling survival", digits = 6, show.icc = FALSE, show.re.var = FALSE, title = "Soil cations at 5m scale")
```

<br>
<br>
<br>
<br>

### ELEVATION at 10m scale

```{r}
surv$BAtot10 <- surv$BAc10 + surv$BAh10
surv$BAtot10_d <- surv$BAtot10 / (pi*(10^2))
surv$BAc10_d <- surv$BAc10 / (pi*(10^2))
surv$BAh10_d <- surv$BAh10 / (pi*(10^2))

surv <- surv %>% group_by(species) %>% mutate(BAc10_d = scale(BAc10_d))
surv$BAc10_d <- ifelse(is.na(surv$BAc10_d), 0, surv$BAc10_d)
surv <- surv %>% ungroup()

toscale <- c("BAh10_d", "BAtot10_d")
surv[, toscale] <- scale(surv[, toscale])
```

```{r, include = FALSE}
# run all competing models
elev.tot.add10 <- update(elev.null, .~. + BAtot10_d)
elev.sep.add10 <- update(elev.null, .~. + BAh10_d + BAc10_d)
elev.tot.int10 <- update(elev.null, .~. + elev*BAtot10_d)
elev.sep.int10 <- update(elev.null, .~. + elev*BAh10_d + elev*BAc10_d)
```

```{r, message = FALSE}
comp.tab.elev10 <- AIC(elev.null, elev.tot.add10, elev.sep.add10, elev.tot.int10, elev.sep.int10)
comp.tab.elev10$delta_AIC <- comp.tab.elev10$AIC - min(comp.tab.elev10$AIC)
comp.tab.elev10 <- cbind(comp.tab.elev10, 
                        BIC(elev.null, elev.tot.add10, elev.sep.add10, elev.tot.int10, elev.sep.int10)[2])
comp.tab.elev10$delta_BIC <- comp.tab.elev10$BIC - min(comp.tab.elev10$BIC)
kable(comp.tab.elev10)
```

```{r, message = FALSE}
# Report model results from best-performing model
tab_model(elev.sep.add10, pred.labels = c("(Intercept)", "Diameter", "Elevation", "Het BA at 10m", "Con BA at 10m"), dv.labels = "Sapling survival", digits = 6, show.icc = FALSE, show.re.var = FALSE, title = "Elevation at 10m scale")
```

<br>
<br>

### GAP MEASURE at 10m scale

```{r, include = FALSE}
# run all competing models
gap.tot.add10 <- update(gap.null, .~. + BAtot10_d)
gap.sep.add10 <- update(gap.null, .~. + BAh10_d + BAc10_d)
gap.tot.int10 <- update(gap.null, .~. + gap*BAtot10_d)
gap.sep.int10 <- update(gap.null, .~. + gap*BAh10_d + gap*BAc10_d)
```

```{r, message = FALSE}
comp.tab.gap10 <- AIC(gap.null, gap.tot.add10, gap.sep.add10, gap.tot.int10, gap.sep.int10)
comp.tab.gap10$delta_AIC <- comp.tab.gap10$AIC - min(comp.tab.gap10$AIC)
comp.tab.gap10 <- cbind(comp.tab.gap10, 
                        BIC(gap.null, gap.tot.add10, gap.sep.add10, gap.tot.int10, gap.sep.int10)[2])
comp.tab.gap10$delta_BIC <- comp.tab.gap10$BIC - min(comp.tab.gap10$BIC)
kable(comp.tab.gap10)
```

```{r, message = FALSE}
# Report model results from best-performing model
tab_model(gap.sep.add10, pred.labels = c("(Intercept)", "Diameter", "Gap", "Het BA at 10m", "Con BA at 10m"), dv.labels = "Sapling survival", digits = 6, show.icc = FALSE, show.re.var = FALSE, title = "Gap measure at 10m scale")
```

<br>
<br>

### SOIL ORGANIC MATTER at 10m scale

```{r, include = FALSE}
# run all competing models
org.tot.add10 <- update(org.null, .~. + BAtot10_d)
org.sep.add10 <- update(org.null, .~. + BAh10_d + BAc10_d)
org.tot.int10 <- update(org.null, .~. + org*BAtot10_d)
org.sep.int10 <- update(org.null, .~. + org*BAh10_d + org*BAc10_d)
```

```{r, message = FALSE}
comp.tab.org10 <- AIC(org.null, org.tot.add10, org.sep.add10, org.tot.int10, org.sep.int10)
comp.tab.org10$delta_AIC <- comp.tab.org10$AIC - min(comp.tab.org10$AIC)
comp.tab.org10 <- cbind(comp.tab.org10, 
                        BIC(org.null, org.tot.add10, org.sep.add10, org.tot.int10, org.sep.int10)[2])
comp.tab.org10$delta_BIC <- comp.tab.org10$BIC - min(comp.tab.org10$BIC)
kable(comp.tab.org10)
```

```{r, message = FALSE}
# Report model results from best-performing model
tab_model(org.sep.add10, pred.labels = c("(Intercept)", "Diameter", "Organic", "Het BA at 10m", "Con BA at 10m"), dv.labels = "Sapling survival", digits = 6, show.icc = FALSE, show.re.var = FALSE, title = "Soil organic matter at 10m scale")
```

<br>
<br>

### CATIONS at 10m scale

```{r, include = FALSE}
# run all competing models
cations.tot.add10 <- update(cations.null, .~. + BAtot10_d)
cations.sep.add10 <- update(cations.null, .~. + BAh10_d + BAc10_d)
cations.tot.int10 <- update(cations.null, .~. + cations*BAtot10_d)
cations.sep.int10 <- update(cations.null, .~. + cations*BAh10_d + cations*BAc10_d)
```

```{r, message = FALSE}
comp.tab.cations10 <- AIC(cations.null, cations.tot.add10, cations.sep.add10, cations.tot.int10, cations.sep.int10)
comp.tab.cations10$delta_AIC <- comp.tab.cations10$AIC - min(comp.tab.cations10$AIC)
comp.tab.cations10 <- cbind(comp.tab.cations10, 
                        BIC(cations.null, cations.tot.add10, cations.sep.add10, cations.tot.int10, cations.sep.int10)[2])
comp.tab.cations10$delta_BIC <- comp.tab.cations10$BIC - min(comp.tab.cations10$BIC)
kable(comp.tab.cations10)
```

```{r, message = FALSE}
# Report model results from best-performing model
tab_model(cations.sep.add10, pred.labels = c("(Intercept)", "Diameter", "Cations", "Het BA at 10m", "Con BA at 10m"), dv.labels = "Sapling survival", digits = 6, show.icc = FALSE, show.re.var = FALSE, title = "Soil cations at 10m scale")
```

<br>
<br>
<br>
<br>

### ELEVATION at 15m scale

```{r}
surv$BAtot15 <- surv$BAc15 + surv$BAh15
surv$BAtot15_d <- surv$BAtot15 / (pi*(15^2))
surv$BAc15_d <- surv$BAc15 / (pi*(15^2))
surv$BAh15_d <- surv$BAh15 / (pi*(15^2))

surv <- surv %>% group_by(species) %>% mutate(BAc15_d = scale(BAc15_d))
surv$BAc15_d <- ifelse(is.na(surv$BAc15_d), 0, surv$BAc15_d)
surv <- surv %>% ungroup()

toscale <- c("BAh15_d", "BAtot15_d")
surv[, toscale] <- scale(surv[, toscale])
```

```{r, include = FALSE}
# run all competing models
elev.tot.add15 <- update(elev.null, .~. + BAtot15_d)
elev.sep.add15 <- update(elev.null, .~. + BAh15_d + BAc15_d)
elev.tot.int15 <- update(elev.null, .~. + elev*BAtot15_d)
elev.sep.int15 <- update(elev.null, .~. + elev*BAh15_d + elev*BAc15_d)
```

```{r, message = FALSE}
comp.tab.elev15 <- AIC(elev.null, elev.tot.add15, elev.sep.add15, elev.tot.int15, elev.sep.int15)
comp.tab.elev15$delta_AIC <- comp.tab.elev15$AIC - min(comp.tab.elev15$AIC)
comp.tab.elev15 <- cbind(comp.tab.elev15, 
                        BIC(elev.null, elev.tot.add15, elev.sep.add15, elev.tot.int15, elev.sep.int15)[2])
comp.tab.elev15$delta_BIC <- comp.tab.elev15$BIC - min(comp.tab.elev15$BIC)
kable(comp.tab.elev15)
```

```{r, message = FALSE}
# Report model results from best-performing model
tab_model(elev.null, pred.labels = c("(Intercept)", "Diameter", "Elevation"), dv.labels = "Sapling survival", digits = 6, show.icc = FALSE, show.re.var = FALSE, title = "Elevation at 15m scale")
```

<br>
<br>

### GAP MEASURE at 15m scale

```{r, include = FALSE}
# run all competing models
gap.tot.add15 <- update(gap.null, .~. + BAtot15_d)
gap.sep.add15 <- update(gap.null, .~. + BAh15_d + BAc15_d)
gap.tot.int15 <- update(gap.null, .~. + gap*BAtot15_d)
gap.sep.int15 <- update(gap.null, .~. + gap*BAh15_d + gap*BAc15_d)
```

```{r, message = FALSE}
comp.tab.gap15 <- AIC(gap.null, gap.tot.add15, gap.sep.add15, gap.tot.int15, gap.sep.int15)
comp.tab.gap15$delta_AIC <- comp.tab.gap15$AIC - min(comp.tab.gap15$AIC)
comp.tab.gap15 <- cbind(comp.tab.gap15, 
                        BIC(gap.null, gap.tot.add15, gap.sep.add15, gap.tot.int15, gap.sep.int15)[2])
comp.tab.gap15$delta_BIC <- comp.tab.gap15$BIC - min(comp.tab.gap15$BIC)
kable(comp.tab.gap15)
```

```{r, message = FALSE}
# Report model results from best-performing model
tab_model(gap.null, pred.labels = c("(Intercept)", "Diameter", "Gap"), dv.labels = "Sapling survival", digits = 6, show.icc = FALSE, show.re.var = FALSE, title = "Gap measure at 15m scale")
```

<br>
<br>

### SOIL ORGANIC MATTER at 15m scale

```{r, include = FALSE}
# run all competing models
org.tot.add15 <- update(org.null, .~. + BAtot15_d)
org.sep.add15 <- update(org.null, .~. + BAh15_d + BAc15_d)
org.tot.int15 <- update(org.null, .~. + org*BAtot15_d)
org.sep.int15 <- update(org.null, .~. + org*BAh15_d + org*BAc15_d)
```

```{r, message = FALSE}
comp.tab.org15 <- AIC(org.null, org.tot.add15, org.sep.add15, org.tot.int15, org.sep.int15)
comp.tab.org15$delta_AIC <- comp.tab.org15$AIC - min(comp.tab.org15$AIC)
comp.tab.org15 <- cbind(comp.tab.org15, 
                        BIC(org.null, org.tot.add15, org.sep.add15, org.tot.int15, org.sep.int15)[2])
comp.tab.org15$delta_BIC <- comp.tab.org15$BIC - min(comp.tab.org15$BIC)
kable(comp.tab.org15)
```

```{r, message = FALSE}
# Report model results from best-performing model
tab_model(org.null, pred.labels = c("(Intercept)", "Diameter", "Organic"), dv.labels = "Sapling survival", digits = 6, show.icc = FALSE, show.re.var = FALSE, title = "Soil organic matter at 15m scale")
```

<br>
<br>

### CATIONS at 15m scale

```{r, include = FALSE}
# run all competing models
cations.tot.add15 <- update(cations.null, .~. + BAtot15_d)
cations.sep.add15 <- update(cations.null, .~. + BAh15_d + BAc15_d)
cations.tot.int15 <- update(cations.null, .~. + cations*BAtot15_d)
cations.sep.int15 <- update(cations.null, .~. + cations*BAh15_d + cations*BAc15_d)
```

```{r, message = FALSE}
comp.tab.cations15 <- AIC(cations.null, cations.tot.add15, cations.sep.add15, cations.tot.int15, cations.sep.int15)
comp.tab.cations15$delta_AIC <- comp.tab.cations15$AIC - min(comp.tab.cations15$AIC)
comp.tab.cations15 <- cbind(comp.tab.cations15, 
                        BIC(cations.null, cations.tot.add15, cations.sep.add15, cations.tot.int15, cations.sep.int15)[2])
comp.tab.cations15$delta_BIC <- comp.tab.cations15$BIC - min(comp.tab.cations15$BIC)
kable(comp.tab.cations15)
```

```{r, message = FALSE}
# Report model results from best-performing model
tab_model(cations.null, pred.labels = c("(Intercept)", "Diameter", "Cations"), dv.labels = "Sapling survival", digits = 6, show.icc = FALSE, show.re.var = FALSE, title = "Soil cations at 15m scale")
```

<br>
<br>
<br>
<br>

### ELEVATION at 20m scale

```{r}
surv$BAtot20 <- surv$BAc20 + surv$BAh20
surv$BAtot20_d <- surv$BAtot20 / (pi*(20^2))
surv$BAc20_d <- surv$BAc20 / (pi*(20^2))
surv$BAh20_d <- surv$BAh20 / (pi*(20^2))

surv <- surv %>% group_by(species) %>% mutate(BAc20_d = scale(BAc20_d))
surv$BAc20_d <- ifelse(is.na(surv$BAc20_d), 0, surv$BAc20_d)
surv <- surv %>% ungroup()

toscale <- c("BAh20_d", "BAtot20_d")
surv[, toscale] <- scale(surv[, toscale])
```

```{r, include = FALSE}
# run all competing models
elev.tot.add20 <- update(elev.null, .~. + BAtot20_d)
elev.sep.add20 <- update(elev.null, .~. + BAh20_d + BAc20_d)
elev.tot.int20 <- update(elev.null, .~. + elev*BAtot20_d)
elev.sep.int20 <- update(elev.null, .~. + elev*BAh20_d + elev*BAc20_d)
```

```{r, message = FALSE}
comp.tab.elev20 <- AIC(elev.null, elev.tot.add20, elev.sep.add20, elev.tot.int20, elev.sep.int20)
comp.tab.elev20$delta_AIC <- comp.tab.elev20$AIC - min(comp.tab.elev20$AIC)
comp.tab.elev20 <- cbind(comp.tab.elev20, 
                        BIC(elev.null, elev.tot.add20, elev.sep.add20, elev.tot.int20, elev.sep.int20)[2])
comp.tab.elev20$delta_BIC <- comp.tab.elev20$BIC - min(comp.tab.elev20$BIC)
kable(comp.tab.elev20)
```

```{r, message = FALSE}
# Report model results from best-performing model
tab_model(elev.null, pred.labels = c("(Intercept)", "Diameter", "Elevation"), dv.labels = "Sapling survival", digits = 6, show.icc = FALSE, show.re.var = FALSE, title = "Elevation at 20m scale")
```

<br>
<br>

### GAP MEASURE at 20m scale

```{r, include = FALSE}
# run all competing models
gap.tot.add20 <- update(gap.null, .~. + BAtot20_d)
gap.sep.add20 <- update(gap.null, .~. + BAh20_d + BAc20_d)
gap.tot.int20 <- update(gap.null, .~. + gap*BAtot20_d)
gap.sep.int20 <- update(gap.null, .~. + gap*BAh20_d + gap*BAc20_d)
```

```{r, message = FALSE}
comp.tab.gap20 <- AIC(gap.null, gap.tot.add20, gap.sep.add20, gap.tot.int20, gap.sep.int20)
comp.tab.gap20$delta_AIC <- comp.tab.gap20$AIC - min(comp.tab.gap20$AIC)
comp.tab.gap20 <- cbind(comp.tab.gap20, 
                        BIC(gap.null, gap.tot.add20, gap.sep.add20, gap.tot.int20, gap.sep.int20)[2])
comp.tab.gap20$delta_BIC <- comp.tab.gap20$BIC - min(comp.tab.gap20$BIC)
kable(comp.tab.gap20)
```

```{r, message = FALSE}
# Report model results from best-performing model
tab_model(gap.null, pred.labels = c("(Intercept)", "Diameter", "Gap"), dv.labels = "Sapling survival", digits = 6, show.icc = FALSE, show.re.var = FALSE, title = "Gap measure at 20m scale")
```

<br>
<br>

### SOIL ORGANIC MATTER at 20m scale

```{r, include = FALSE}
# run all competing models
org.tot.add20 <- update(org.null, .~. + BAtot20_d)
org.sep.add20 <- update(org.null, .~. + BAh20_d + BAc20_d)
org.tot.int20 <- update(org.null, .~. + org*BAtot20_d)
org.sep.int20 <- update(org.null, .~. + org*BAh20_d + org*BAc20_d)
```

```{r, message = FALSE}
comp.tab.org20 <- AIC(org.null, org.tot.add20, org.sep.add20, org.tot.int20, org.sep.int20)
comp.tab.org20$delta_AIC <- comp.tab.org20$AIC - min(comp.tab.org20$AIC)
comp.tab.org20 <- cbind(comp.tab.org20, 
                        BIC(org.null, org.tot.add20, org.sep.add20, org.tot.int20, org.sep.int20)[2])
comp.tab.org20$delta_BIC <- comp.tab.org20$BIC - min(comp.tab.org20$BIC)
kable(comp.tab.org20)
```

```{r, message = FALSE}
# Report model results from best-performing model
tab_model(org.null, pred.labels = c("(Intercept)", "Diameter", "Organic"), dv.labels = "Sapling survival", digits = 6, show.icc = FALSE, show.re.var = FALSE, title = "Soil organic matter at 20m scale")
```

<br>
<br>

### CATIONS at 20m scale

```{r, include = FALSE}
# run all competing models
cations.tot.add20 <- update(cations.null, .~. + BAtot20_d)
cations.sep.add20 <- update(cations.null, .~. + BAh20_d + BAc20_d)
cations.tot.int20 <- update(cations.null, .~. + cations*BAtot20_d)
cations.sep.int20 <- update(cations.null, .~. + cations*BAh20_d + cations*BAc20_d)
```

```{r, message = FALSE}
comp.tab.cations20 <- AIC(cations.null, cations.tot.add20, cations.sep.add20, cations.tot.int20, cations.sep.int20)
comp.tab.cations20$delta_AIC <- comp.tab.cations20$AIC - min(comp.tab.cations20$AIC)
comp.tab.cations20 <- cbind(comp.tab.cations20, 
                        BIC(cations.null, cations.tot.add20, cations.sep.add20, cations.tot.int20, cations.sep.int20)[2])
comp.tab.cations20$delta_BIC <- comp.tab.cations20$BIC - min(comp.tab.cations20$BIC)
kable(comp.tab.cations20)
```

```{r, message = FALSE}
# Report model results from best-performing model
tab_model(cations.null, pred.labels = c("(Intercept)", "Diameter", "Cations"), dv.labels = "Sapling survival", digits = 6, show.icc = FALSE, show.re.var = FALSE, title = "Soil cations at 20m scale")
```

<br>
<br>
<br>
<br>

TESTING FOR SPATIAL AUTOCORRELATION

```{r, message = FALSE}
ge.vgm <- variogram(resid(elev.sep.int5)~1, loc= ~X+Y, data = surv)
gg.vgm <- variogram(resid(gap.sep.add5)~1, loc= ~X+Y, data = surv)
go.vgm <- variogram(resid(org.sep.add5)~1, loc= ~X+Y, data = surv)
gf.vgm <- variogram(resid(cations.sep.add5)~1, loc= ~X+Y, data = surv)

plot(ge.vgm, main="Elevation, 5m scale")
plot(gg.vgm, main="Gap measure, 5m scale")
plot(go.vgm, main="Soil organic matter, 5m scale")
plot(gf.vgm, main="Cations, 5m scale")


ge.vgm <- variogram(resid(elev.sep.add10)~1, loc= ~X+Y, data = surv)
gg.vgm <- variogram(resid(gap.sep.add10)~1, loc= ~X+Y, data = surv)
go.vgm <- variogram(resid(org.sep.add10)~1, loc= ~X+Y, data = surv)
gf.vgm <- variogram(resid(cations.sep.add10)~1, loc= ~X+Y, data = surv)

plot(ge.vgm, main="Elevation, 10m scale")
plot(gg.vgm, main="Gap measure, 10m scale")
plot(go.vgm, main="Soil organic matter, 10m scale")
plot(gf.vgm, main="Cations, 10m scale")


ge.vgm <- variogram(resid(elev.null)~1, loc= ~X+Y, data = surv)
gg.vgm <- variogram(resid(gap.null)~1, loc= ~X+Y, data = surv)
go.vgm <- variogram(resid(org.null)~1, loc= ~X+Y, data = surv)
gf.vgm <- variogram(resid(cations.null)~1, loc= ~X+Y, data = surv)

plot(ge.vgm, main="Elevation, Null model")
plot(gg.vgm, main="Gap measure, Null model")
plot(go.vgm, main="Soil organic matter, Null model")
plot(gf.vgm, main="Cations, Null model")
```

